A practical guide to Digital Micro-mirror Devices (DMDs) for wavefront shaping

### 2023-11-29 paper/main.tex
add data section
add abstract

\begin{abstract}
  Abstract
\end{abstract}

@@

>>>>

\begin{abstract}
  Digital micromirror devices have gained popularity in wavefront shaping,
  offering a high frame rate alternative to liquid crystal spatial light modulators.
  They are relatively inexpensive, offer high resolution,
  are easy to operate, and a single device can be used in a broad optical bandwidth.
  However, some technical drawbacks must be considered
  to achieve optimal performance.
  These issues, often undocumented by manufacturers,
  mostly stem from the device's original design for video projection applications.
  Herein, we present a guide to characterize and mitigate these effects.
  Our focus is on providing simple and practical solutions
  that can be easily incorporated into a typical wavefront shaping setup.
\end{abstract}

@@

\section*{Data and code availability}

\noindent Data and code examples are available in the dedicated repository~\cite{github}.
